% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{comment}
\usepackage{tocloft}
\usepackage{lipsum}
\usepackage{array}

\pagenumbering{arabic}
%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands

\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Ross Jacobucci} & \textbf{Curriculum Vitae} \\
118 Haggar Hall  & rjacobuc@nd.edu \\
Notre Dame, Indiana 46556 & rjacobucci.com \\
574-631-2589 & Skype: ross.jacobucci

\end{tabular*}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional History \& Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% problem w/ \ressubheading
\begin{itemize}
	\item
	\ressubheading{Assistant Professor of Psychology}{2017 - Current} {University of Notre Dame}  {Notre Dame, Indiana}
%
\item
	\ressubheading{Ph.D. Psychology} {August 2017}{University of Southern California (USC)}  {Los Angeles, California}
	\begin{itemize}
		\resitem{Area: Quantitative Methods}
		\resitem{Dissertation: Evaluating the Stability of Decision Tree Algorithms.}
	\end{itemize}
\item
\ressubheading{M.A. Psychology} {December 2015}{University of Southern California (USC)}  {Los Angeles, California}
\begin{itemize}
	\resitem{Area: Quantitative Methods}
	\resitem{Thesis: Regularized Structural Equation Modeling.}
\end{itemize}
\item
	\ressubheading{M.A. Psychology}{2011-2013}{University of Northern Iowa (UNI)}{Cedar Falls, Iowa}
	\begin{itemize}
		\resitem{Individualized Study: Quantitative Emphasis}
	\end{itemize}

\item
	\ressubheading{B.A. Psychology}{June 2010}{Luther College}{Decorah, Iowa}
	\begin{itemize}
		\resitem{Thesis: The Effect of Mental Imagery on Performance in Golf.}
	%	\resitem{Cum Laude}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Funding}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize} 
	\setlength{\topsep}{0pt}%
	\setlength{\leftmargin}{0.1in}%
	\setlength{\listparindent}{-0.1in}%
	\setlength{\itemindent}{-0.2in}%
	\setlength{\parsep}{\parskip}%
	\begin{comment}		
	\item {\textbf{\large{Pending}}}
	
	
	\begin{center}
	\parbox{6.5in}{{Ross Jacobucci (PI) }   \hspace{9cm} Under Review}
	\parbox{6.5in}{\textbf{IES Statistical and Research Methodology in Education: Early Career Grant} }
	\parbox{6.5in}{\textit{Extending Regularized Structural Equation Modeling for Big Data in Education Research}}
	\parbox{6.5in}{Total Direct: \$139,759}
	\end{center}
	
	\begin{center}
	\parbox{6.5in}{{Ross Jacobucci (Co-PI) \& Brooke Ammerman (Co-PI)}   \hspace{3.8cm} Under Review}
	\parbox{6.5in}{\textbf{NIH 1R03MH120488-01} }
	\parbox{6.5in}{\textit{The Implementation and Validation of Integrative Machine Learning for Predicting Suicide Outcomes}}
	\parbox{6.5in}{Total Direct: \$99,188}
	\end{center}
	\end{comment}	
	
	
	\item{\textbf{\large{Ongoing}}}
	
	\begin{center}
		\parbox{6.5in}{{Ross Jacobucci (PI) }   \hspace{9cm} Academic Year 2018-2019}
		\parbox{6.5in}{Small Research and Creative Work grant}
		\parbox{6.5in}{\textbf{Institute for Scholarship in the Liberal Arts (ND)} }
		\parbox{6.5in}{\textit{Text Analysis for the Prediction of Suicide: A Pilot Study}}
		\parbox{6.5in}{\$2,475}
	\end{center}
	
	
	
	\begin{center}
		\parbox{6.5in}{{Ross Jacobucci (Co-PI) \& Brooke Ammerman (Co-PI)}   \hspace{3.8cm} 8/13/18-8/13/20}
		\parbox{6.5in}{\textbf{Advanced Diagnostics and Therapeutics Discovery Fund.} }
		\parbox{6.5in}{\textit{Using Integrative Data Mining to Improve the Prediction of Suicide: An Initial Application.}}
		\parbox{6.5in}{Total Direct: \$41,068}
	\end{center}
	
	\begin{comment}
	\begin{center}
	\parbox{6.5in}{{Evan Kleiman (PI)}    \hspace{9.2cm} 6/26/18-12/26/19}
	\parbox{6.5in}{\textbf{Military Suicide Research Consortium Common Data Elements} }
	\parbox{6.5in}{\textit{Enhancing Identification of Suicide Risk among Military Service Members and Veterans: A Machine Learning Approach to Suicidality.}}
	\parbox{6.5in}{\textbf{Role: Consultant}}
	\end{center}
	
	
	\item{\textbf{\large{Completed}}}
	
	\begin{center}
	\parbox{6.5in}{{T32 AG000037-38  \hspace{1cm} Crimmins (PI)}   \hspace{6.1cm} 01/01/15-07/31/17}
	\parbox{6.5in}{\textbf{Sponsored: Ruth L. Kirschstein National Research Service Award (T32).}}
	\parbox{6.5in}{\textit{Predoctoral trainee on the Multidisciplinary Research Training in Gerontology Grant at USC. }}
	\parbox{6.5in}{Role: Predoctoral Trainee}
	\end{center}
	%
	
	\item{\textbf{\large{Not Funded}}}
	
	\begin{center}
	\parbox{6.5in}{{Ross Jacobucci (PI)} }
	\parbox{6.5in}{\textbf{NIH 1R01MH117597-01} }
	\parbox{6.5in}{\textit{Integrative Data Mining in the Prediction of the Pathway to Suicide.}}
	\parbox{6.5in}{Total Direct: \$540,750}
	\end{center}
	\end{comment}	
	
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize} 
	\setlength{\topsep}{0pt}%
	\setlength{\leftmargin}{0.1in}%
	\setlength{\listparindent}{-0.1in}%
	\setlength{\itemindent}{-0.2in}%
	\setlength{\parsep}{\parskip}%
	
	\item {\textbf{\large{Publications}}}
	%
	\item[] Ammerman, B. A., Hong, M., Sorgi, K. M., \textbf{Jacobucci, R.}, Park, Y., \& McCloskey, M. S. (accepted). An examination of individual forms of nonsuicidal self-injury. \emph{Psychiatry Research}.
	%
	\item[] \textbf{Jacobucci, R.}, Serang, S., \& Grimm, K. J. (accepted). A short note on complications in interpretation with the dual change score model . \emph{Structural Equation Modeling}.
	% 
	\item[]Serang, S. \& \textbf{Jacobucci, R.} (in press). Exploratory mediation analysis of dichotomous outcomes via regularization. \emph{Multivariate Behavioral Research}.
	%
	\item[] Burke, T.A., Ammerman, B.A., \& \textbf{Jacobucci, R.} (in press). The use of machine learning in the study of suicidal and non-suicidal self-injurious thoughts and behavior: A systematic review. \emph{Journal of Affective Disorders.}
	%
	\item[] Ammerman, B.A., \textbf{Jacobucci, R.} \& McCloskey, M.S. (2019). Re-considering important outcomes of the NSSI disorder diagnostic criterion A. \emph{Journal of Clinical Psychology, 75}, 1084-1097.
	% 
	\item[] \textbf{Jacobucci, R.}, Brandmaier, A., \& Kievit, R. (2019). A practical guide to variable selection in structural equation models with regularized MIMIC models. \emph{Advances in Methods and Practices in Psychological Science, 2}, 55-76.  
	%
	\item[] Usami, S., \textbf{Jacobucci, R.}, \& Hayes, T. (2019). The performance of latent growth curve model based structural equation model trees to uncover population heterogeneity in growth trajectories. \emph{Computational Statistics, 34}, 1-22.
	%
	\item[]Ammerman, B. A., Serang, S., \textbf{Jacobucci}, R., Burke, T., A., Alloy, L. B., \& McCloskey, M. S. (2018). Exploratory analysis of mediators in the relationship between childhood maltreatment and suicidal behavior. \emph{Journal of Adolescence, 69, 103-112.}
	%
	\item[]Stegmann, G., \textbf{Jacobucci, R.}, Serang, S., \& Grimm, K. J. (2018). Recursive partitioning with nonlinear change trajectories. \emph{Multivariate Behavioral Research, 53}, 559-570.
	%
	\item[]Burke, T. A., \textbf{Jacobucci, R.}, Ammerman, B. A.,, Piccirillo, M., McCloskey M., \& Alloy, L. B. (2018). Identifying the relative importance of non-suicidal self-injury features in predicting suicidal ideation and behavior using exploratory data mining. \emph{Psychiatry Research, 262,} 175-183.
	%
	\item[]Ammerman, B. A., \textbf{Jacobucci, R.}, \& McCloskey, M. S. (2018). Using exploratory data mining to identify important predictors of non-suicidal self-injury frequency. \emph{Psychology of Violence, 8,} 515-525.
	%
	\item[]Ammerman, B. A., \textbf{Jacobucci, R.}, Kleiman, E. M., Uyeji, L., \& McCloskey, M. S. (2018). The relationship between nonsuicidal self-injury age of onset and severity of self-harm. \emph{Suicide and Life Threatening Behavior, 48,} 31-37.
	%
	\item[] \textbf{Jacobucci, R.}, Grimm, K. J. (2018). Comparison of frequentist and Bayesian regularization in structural equation modeling. \emph{Structural Equation Modeling, 25}, 639-649.
\vspace{3mm}
%
%

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize} 
	\setlength{\topsep}{0pt}%
	\setlength{\leftmargin}{0.1in}%
	\setlength{\listparindent}{-0.1in}%
	\setlength{\itemindent}{-0.2in}%
	\setlength{\parsep}{\parskip}%
	
	
	
	%\item {\textbf{\large{Symposium Chair}}}
	
	%\item[] \emph{Structural Equation Modeling}. 2016 International Meeting for the Psychometric Society, Asheville, North Carolina.
	
	%
	\item {\textbf{\large{Oral Presentations}}}
	%
	\item[] \textbf{Jacobucci, R.} (2019, March). The use text mining for clinical research: An overview of the methodology. Paper submitted for presentation at the 53rd Annual Convention for the Association for Behavioral and Cognitive Therapies, Atlanta, Georgia.
	%
	\item[] Ammerman, B.A., Wilcox, K. T., \& \textbf{Jacobucci, R.} (2019, March) A nuanced examination of the relationship between social connectedness and suicidal ideation. Paper submitted for presentation at the 53rd Annual Convention for the Association for Behavioral and Cognitive Therapies, Atlanta, Georgia.
	
	\item[] Park, Y., O'Loughlin, C. M., \textbf{Jacobucci, R.} , \& Ammerman, B.A. (2019, March). Examining person-specific reasons for living in the prediction of suicidal ideation: A text mining approach. Paper submitted for presentation at the 53rd Annual Convention for the Association for Behavioral and Cognitive Therapies, Atlanta, Georgia.
	
	\item[] Wilcox, K. T., \textbf{Jacobucci, R.} , McCloskey, M. S. \& Ammerman, B.A.(2019, March). Evaluating personal narratives of interpersonal relationships via text mining to predict nonsuicidal self-injury. Paper submitted for presentation at the 53rd Annual Convention for the Association for Behavioral and Cognitive Therapies, Atlanta, Georgia.
	%
	\item[]\textbf{Jacobucci, R.} (2019, May). \emph{Flexible specification of large structural equation models with regularization.} Keynote speech given at the Big Data in Psychology Pre-Conference in Dubrovnik, Croatia.
	%
	\item[]\textbf{Jacobucci, R.} (2019, February). \emph{Novel assessment strategies for improving our understanding of mental health.} Invited talk given at the Quant Methods colloquium at Vanderbilt University.
	
\end{itemize}



\end{document}